\nonstopmode{}
\documentclass[a4paper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8,latin1]{inputenc}
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `BSgenome.MapK10.SRA.SRR060191.3'}}
\par\bigskip{\large \today}
\end{center}
\begin{description}
\raggedright{}
\item[Title]\AsIs{Full genome sequence for Mycobacterium avium subsp.
paratuberculosis str. k10 (updated in 2010)}
\item[Description]\AsIs{Improved annotation and revised full genome sequence of Mycobacterium avium subsp. paratuberculosis str. k10 provided by SRA}
\item[Version]\AsIs{1.0.0}
\item[Author]\AsIs{The Bioconductor Dev Team}
\item[Maintainer]\AsIs{Bioconductor Package Maintainer }\email{maintainer@bioconductor.org}\AsIs{}
\item[Depends]\AsIs{BSgenome (>= 1.50.0)}
\item[Imports]\AsIs{BSgenome}
\item[Suggests]\AsIs{}
\item[License]\AsIs{Artistic-2.0}
\item[organism]\AsIs{Mycobacterium avium subsp. paratuberculosis str. k10}
\item[common\_name]\AsIs{M. avium subsp. paratuberculosis (Map)}
\item[provider]\AsIs{SRA}
\item[provider\_version]\AsIs{SRR060191.3}
\item[release\_date]\AsIs{2010/09}
\item[release\_name]\AsIs{SRR060191}
\item[source\_url]\AsIs{https://sra-downloadb.be-md.ncbi.nlm.nih.gov/sos/sra-pub-run-1/SRR060191/SRR060191.3}
\item[biocViews]\AsIs{AnnotationData, Genetics, BSgenome, Map\_k10}
\end{description}
\Rdcontents{\R{} topics documented:}
\inputencoding{utf8}
\HeaderA{BSgenome.MapK10.SRA.SRR060191.3}{Full genome sequence for Mycobacterium avium subsp. paratuberculosis str. k10 (updated in 2010)}{BSgenome.MapK10.SRA.SRR060191.3}
\aliasA{BSgenome.MapK10.SRA.SRR060191.3-package}{BSgenome.MapK10.SRA.SRR060191.3}{BSgenome.MapK10.SRA.SRR060191.3.Rdash.package}
\aliasA{MapK10}{BSgenome.MapK10.SRA.SRR060191.3}{MapK10}
\keyword{package}{BSgenome.MapK10.SRA.SRR060191.3}
\keyword{data}{BSgenome.MapK10.SRA.SRR060191.3}
%
\begin{Description}\relax
Improved annotation and revised full genome sequence of Mycobacterium avium subsp. paratuberculosis str. k10 provided by SRA
\end{Description}
%
\begin{Note}\relax
This BSgenome data package was made from the following source data files:
\begin{alltt}
-- information not available --
  \end{alltt}


See \code{?\LinkA{BSgenomeForge}{BSgenomeForge}} and the BSgenomeForge
vignette (\code{vignette("BSgenomeForge")}) in the \pkg{BSgenome}
software package for how to make a BSgenome data package.
\end{Note}
%
\begin{Author}\relax
The Bioconductor Dev Team
\end{Author}
%
\begin{SeeAlso}\relax
\begin{itemize}

\item \LinkA{BSgenome}{BSgenome} objects and the
\code{\LinkA{available.genomes}{available.genomes}} function
in the \pkg{BSgenome} software package.
\item \LinkA{DNAString}{DNAString} objects in the \pkg{Biostrings}
package.
\item The BSgenomeForge vignette (\code{vignette("BSgenomeForge")})
in the \pkg{BSgenome} software package for how to make a BSgenome
data package.

\end{itemize}

\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
BSgenome.MapK10.SRA.SRR060191.3
genome <- BSgenome.MapK10.SRA.SRR060191.3
head(seqlengths(genome))


## ---------------------------------------------------------------------
## Genome-wide motif searching
## ---------------------------------------------------------------------
## See the GenomeSearching vignette in the BSgenome software
## package for some examples of genome-wide motif searching using
## Biostrings and the BSgenome data packages:
if (interactive())
    vignette("GenomeSearching", package="BSgenome")
\end{ExampleCode}
\end{Examples}
\printindex{}
\end{document}
